\pkg{plotROC}: A Tool for Plotting ROC Curves

### 2016-07-15 Paper/sachs2015plotROC.tex
revision number two

\title{\pkg{plotROC}: A Better Tool for Plotting ROC Curves}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{ Michael C. Sachs} %% comma-separated
\Plaintitle{plotROC: A Better Tool for Plotting ROC Curves} %% without formatting

\Shorttitle{\pkg{plotROC}: A Better Tool for Plotting ROC Curves} %% a short title (if necessary)
%% an abstract and keywords
\Abstract{
  Plots of the receiver operating characteristic (ROC) curve are
  ubiquitous in medical research. Designed to simultaneously display the
  operating characteristics at every possible value of a continuous
  diagnostic test, ROC curves are used in oncology to evaluate screening,
  diagnostic, prognostic and predictive biomarkers. I reviewed a sample of
  ROC curve plots from the major oncology journals in order to assess
  current trends in usage and design elements. My review suggests that ROC
  curve plots are often ineffective as statistical charts and that poor
  design obscures the relevant information the chart is intended to
  display. I describe my new \proglang{R} package that was created to
  address the shortcomings of existing tools. The package has functions to
  create informative ROC curve plots, with sensible defaults and a simple
  interface, for use in print or as an interactive web-based plot. A web
  application was developed to reach a broader audience of scientists who
  do not use \proglang{R}.
}
\Keywords{ROC curves; graphics; interactive; plots}
\Plainkeywords{ROC curves; graphics; interactive; plots} %% without formatting
%% at least one keyword must be supplied

@@

Given a sample of test and disease status pairs,
\((M_1, D_1), \ldots, (M_n, D_n)\), I can estimate the ROC curve by
computing proportions in the diseased and healthy subgroups separately.
Specifically, given a fixed cutoff \(c\), an estimate of the \(TPF(c)\)
is the proportion of test positives among the diseased subgroup:

@@

where \(1\{\cdot\}\) is the indicator function that equals 1 when the
condition inside the parentheses is true and 0 otherwise. An estimate
for \(FPF(c)\) is the proportion of test positives among the healthy
subgroup and is given by a similar expression with \(D_i = 1\) replaced
with \(D_i = 0\). Calculating these proportions for \(c\) equal to each
unique value of the observed \(M_i\) yields what is known as the
empirical ROC curve estimate. The empirical estimate is a step function.
Other methods exist to estimate the ROC curve, such as the binormal
parametric estimate which can be used to get a smooth curve. There are
also extensions that allow for estimation with time-to-event outcomes
subject to censoring. For a more thorough reference on the methods and
theory surrounding ROC curves, I refer interested readers to
\citet{pepe2003statistical}.

@@

The ROC curve plot is, at the most basic level, a line graph. Therefore,
once the appropriate statistics are estimated, existing plotting
functions can be used to create an ROC curve plot. Viewers can identify
ROC plots through context, by observing the shape of the line, and
through the addition of axis labels, titles, legends, and so on. In my
review of the oncology literature, I observed plots with the distinctive
characteristics of the plotting functions from Microsoft Excel
\citep{excel}, \proglang{SAS} \citep{sas}, \proglang{SPSS} \citep{spss},
and the base \proglang{R} plotting functions \citep{arr}.

There are several \proglang{R} packages related to ROC curve estimation
that contain dedicated plotting functions. The \pkg{ROCR} package
\citep{rocr} plots the FPF \emph{versus} TPF, as usual, and then takes
the interesting approach of encoding the cutoff values as a separate
color scale along the ROC curve itself. A legend for the color scale is
placed along the vertical axis on the right of the plotting region. The
\pkg{pROC} package \citep{pROC} provides an option for plotting cutoff
labels (\code{print.thres = TRUE}) and is mainly focused on estimating
confidence intervals and regions for restricted ranges of the ROC curve.
The plotting methods therein use the base \proglang{R} plotting
functions to create nice displays of the curves along with shaded
confidence regions. My \pkg{plotROC} package uses the \pkg{ggplot2}
\citep{ggplot2} plotting library to create clear, informative ROC plots,
with interactive features for use on the web, and sensible defaults for
use in print.

@@

The panels of Figure \ref{figure1} illustrate the most common styles of
ROC curve plots, and the associated design elements. I favor the use of
gridlines and a diagonal reference line to facilitate accurate readings
off of the axes. Direct labels are preferred over legends because they
omit the additional cognitive step of matching line types or colors to
labels. My \pkg{plotROC} package additionally provides plotting of
cutoff values, which are displayed interactively with the web-based
output option, and direct labels for print use. Exact confidence regions
for points on the ROC curve are optionally calculated and displayed.
Additionally, I use axis scales adjusted to be denser near the margins 0
and 1. In medical applications, it is often necessary to have a very low
FPR (less than 10\%, for instance), therefore the smaller scales are
useful for accurately determining values near the margins. The next
section details the usage of the \pkg{plotROC} \proglang{R} package and
these features.

@@

I created a \pkg{shiny} application \citep{shiny} in order to make the
features more accessible to non-\proglang{R} users. A limited subset of
the functions of \pkg{plotROC} can be performed on an example dataset or
on data that users upload to the website. Resulting plots can be saved
to the users' machine as a pdf or as a stand-alone html file. It can be
used in any modern web browser with no other dependencies at the website
here: http://sachsmc.shinyapps.io/plotROC.

@@

Users can install the latest version of \pkg{plotROC} from github, as
shown below. The package will appear on the Comprehensive \proglang{R}
Archive Network in the near future. It can also be downloaded from
https://github.com/sachsmc/plotROC and installed from source. As of
October 19, 2015, \pkg{plotROC} also requires the development version of
\pkg{ggplot2} also available from github.

\begin{Schunk}
\begin{Sinput}
R> devtools::install_github("hadley/ggplot2")
R> devtools::install_github("sachsmc/plotROC")
R> library(plotROC)
\end{Sinput}
\end{Schunk}

@@

As of version 1.0.1, the \pkg{ggplot2} package \citep{ggplot2} exports
the previously internal functions \code{Geom} and \code{Stat}. This
enables developers to create their own statistical tranformations
(stats) and geometric layers (geoms), while enjoying all of the other
features of \pkg{ggplot2}. We have implemented the empirical ROC curve
estimate and the calculation of exact confidence regions as statistical
transformations: \code{stat_roc} and \code{stat_rocci}, respectively. We
have also defined geometric layers for the ROC curve and confidence
regions for the ROC curve: \code{geom_roc} and \code{geom_rocci},
respectively. For further discussion and details of the grammar of
graphics as implemented in \pkg{ggplot2}, we refer readers to
\citet{wickham2010layered} and the \pkg{ggplot2} vignettes.

To use the ROC geometric layer, I use the \code{ggplot} function to
define the aesthetic mappings, and the \code{geom_roc} function to add
an ROC curve layer. The \code{geom_roc} function requires that the named
aesthetics \code{d} for disease status, and \code{m} for marker be
present in the \code{aes} function call inside \code{ggplot}. By
default, the ROC geom and stat are linked, so that when \code{geom_roc}
is called, \code{stat_roc} does the computation, and when
\code{stat_roc} is called, \code{geom_roc} is used to plot the layer.
The disease status need not be coded as 0/1, but if it is not,
\code{stat_roc} assumes (with a warning) that the lowest value in sort
order signifies disease-free status.

@@

The same objects like \code{basicplot} with Roc and/or Rocci layers can
be treated like any other ggplot objects. It can be printed to display
the figure, and other layers can be added to the plot. We provide the
function \texttt{style\_roc()} which is a layer containing a theme,
modified gridlines, and axes. Adding the \texttt{style\_roc()} layer to
the ggplot object creates a plot with sensible defaults for use in
print. This function has options for the number and location of major
and minor breaks, addition of the diagonal guideline, axis labels, and
any theme object created for use with ggplot2 can be supplied.

@@

\begin{Schunk}
\begin{Sinput}
R> library(survivalROC)
R> survT <- rexp(350, 1/5)
R> cens <- rbinom(350, 1, .1)
R> M <- -8 * sqrt(survT) + rnorm(350, sd = survT)
R> sroc <- lapply(c(2, 5, 10), function(t){ 
+   stroc <- survivalROC(Stime = survT, status = cens, marker = M, 
+                        predict.time = t, method = "NNE", 
+                        span = .25 * 350^(-.2))
+   data.frame(TPF = stroc[["TP"]], FPF = stroc[["FP"]], 
+              c = stroc[["cut.values"]], 
+              time = rep(stroc[["predict.time"]], 
+                         length(stroc[["FP"]])))
+   })
R> 
R> sroclong <- do.call(rbind, sroc)
R> 
R> survplot <- ggplot(sroclong, aes(x = FPF, y = TPF, label = c, color = time)) + 
+   geom_roc(labels = FALSE, stat = "identity")
\end{Sinput}
\end{Schunk}

@@

\pkg{plotROC} makes interactive plots by first converting the
\code{ggplot} object into a scalable vector graphic (svg) object with
the \code{gridSVG::grid.export} function. This function maps each
element of the plot to a corresponding element of the svg markup
language. I keep track of the names of the points and labels elements so
that I can add interactivity using \pkg{d3.js} and
\proglang{JavaScript}. The main interactive feature I wanted was to be
able to display the cutoff labels at the points on the ROC curve closest
to the mouse cursor.

There are many ways to solve this with \pkg{d3.js}, but I decided to use
Voronoi polygons to map the cursor location to the nearest point on the
ROC curve. The idea is that for the set of cutoff points along the ROC
curve, the \code{d3.geom.voronoi} function chain computes a set of
polygons overlaying the plotting region such that the area of each
polygon contains the region of the plot closest to it's corresponding
cutoff point. Hover events are bound to the polygons so that when the
mouse cursor moves around the plotting region, the closest point on the
ROC curve is made visible. Similarly, click events are bound to the
polygons so that the appropriate confidence region is made visible upon
clicking. The svg code and all necessary \proglang{JavaScript} code is
returned in the character string provided by
\code{export_interactive_roc}.

This approach is similar to what is done in the \pkg{gridSVG}
\code{grid.animate} function, which uses the svg \code{<animate />}
tags. However, the available features were not sufficient for my needs,
which is why I used \pkg{d3.js}. There are several other \proglang{R}
packages that aim to create interactive figures. The authors of
\pkg{animint} \citep{animint} created an extensive \proglang{JavaScript}
library that creates plots in a similar way as \pkg{ggplot2}. A set of
interactive features can be added to plots using \pkg{d3.js}.
\pkg{ggvis} \citep{ggvis}, \pkg{rCharts} \citep{rcharts}, and the more
recently released \pkg{htmlwidgets} \citep{htmlwidgets} all leverage
existing charting libraries written in \proglang{JavaScript}.
\pkg{qtlcharts} \citep{qtlcharts} uses a set of custom
\proglang{JavaScript} and \pkg{d3.js} functions to visualize data from
genetic experiments. Their general approach is to manipulate the data
and create options in \proglang{R}, and then let the charting libraries
or functions handle the rendering and interactivity. \pkg{plotROC} lets
\proglang{R} do the rendering, allowing the figures to be consistent
across print and web-based media, and retaining the distinctive
\proglang{R} style. This also allows users to manipulate the figures
directly in \proglang{R} to suit their needs, using tools that are more
accessible and familiar to most \proglang{R} users. Then, the
\proglang{JavaScript} adds a layer of interactivity to the rendered
figures.

@@

\begin{Schunk}
\begin{Sinput}
R> sessionInfo()
\end{Sinput}
\begin{Soutput}
R version 3.2.2 (2015-08-14)
Platform: x86_64-apple-darwin13.4.0 (64-bit)
Running under: OS X 10.10.5 (Yosemite)

@@

other attached packages:
[1] survivalROC_1.0.3  tikzDevice_0.8.1   plotROC_2.0.0     
[4] ggplot2_1.0.1.9003 xtable_1.7-4       stringr_1.0.0     
[7] knitr_1.11

loaded via a namespace (and not attached):
 [1] Rcpp_0.12.1      digest_0.6.8     grid_3.2.2       plyr_1.8.3      
 [5] gtable_0.1.2     formatR_1.2.1    magrittr_1.5     evaluate_0.8    
 [9] scales_0.3.0     highr_0.5.1      stringi_0.5-5    labeling_0.3    
[13] tools_3.2.2      munsell_0.4.2    colorspace_1.2-6 filehash_2.3    
\end{Soutput}
\end{Schunk}

>>>>

\title{\pkg{plotROC}: A Tool for Plotting ROC Curves}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{ Michael C. Sachs} %% comma-separated
\Plaintitle{plotROC: A Tool for Plotting ROC Curves} %% without formatting

\Shorttitle{\pkg{plotROC}: A Tool for Plotting ROC Curves} %% a short title (if necessary)
%% an abstract and keywords
\Abstract{
  Plots of the receiver operating characteristic (ROC) curve are
  ubiquitous in medical research. Designed to simultaneously display the
  operating characteristics at every possible value of a continuous
  diagnostic test, ROC curves are used in oncology to evaluate screening,
  diagnostic, prognostic and predictive biomarkers. I reviewed a sample of
  ROC curve plots from the major oncology journals in order to assess
  current trends in usage and design elements. My review suggests that ROC
  curve plots are often ineffective as statistical charts and that poor
  design obscures the relevant information the chart is intended to
  display. I describe my new \proglang{R} package that was created to
  address the shortcomings of existing tools. The package has functions to
  create informative ROC curve plots, with sensible defaults and a simple
  interface, for use in print or as an interactive web-based plot. A web
  application was developed to reach a broader audience of scientists who
  do not use \proglang{R}.
}
\Keywords{ROC curves; graphics; interactive; plots}
\Plainkeywords{ROC curves; graphics; interactive; plots} %% without formatting
%% at least one keyword must be supplied

@@

Given a sample of test and disease status pairs,
\((M_1, D_1), \ldots, (M_n, D_n)\), one can estimate the ROC curve by
computing proportions in the diseased and healthy subgroups separately.
Specifically, given a fixed cutoff \(c\), an estimate of the \(TPF(c)\)
is the proportion of test positives among the diseased subgroup:

@@

where \(1\{\cdot\}\) is the indicator function that equals 1 when the
condition inside the parentheses is true and 0 otherwise. An estimate
for \(FPF(c)\) is the proportion of test positives among the healthy
subgroup and is given by a similar expression with \(D_i = 1\) replaced
with \(D_i = 0\). Calculating these proportions for \(c\) equal to each
unique value of the observed \(M_i\) yields what is known as the
empirical ROC curve estimate. The empirical estimate is a step function.
Other methods exist to estimate the ROC curve, such as the binormal
parametric estimate which can be used to get a smooth curve. There are
also extensions that allow for estimation with time-to-event outcomes
subject to censoring. For a more thorough reference on the methods and
theory surrounding ROC curves, interested readers may look to
\citet{pepe2003statistical}.

@@

The ROC curve plot is, at the most basic level, a line graph. Therefore,
once the appropriate statistics are estimated, existing plotting
functions can be used to create an ROC curve plot. Viewers can identify
ROC plots through context, by observing the shape of the line, and
through the addition of axis labels, titles, legends, and so on. In a
review of the oncology literature, I observed plots with the distinctive
characteristics of the plotting functions from Microsoft Excel
\citep{excel}, \proglang{SAS} \citep{sas}, \proglang{SPSS} \citep{spss},
and the base \proglang{R} plotting functions \citep{arr}.

There are several \proglang{R} packages related to ROC curve estimation
that contain dedicated plotting functions. The \pkg{ROCR} package
\citep{rocr} plots the FPF \emph{versus} TPF, as usual, and then takes
the interesting approach of encoding the cutoff values as a separate
color scale along the ROC curve itself. A legend for the color scale is
placed along the vertical axis on the right of the plotting region. The
\pkg{pROC} package \citep{pROC} provides an option for plotting cutoff
labels (\code{print.thres = TRUE}) and is mainly focused on estimating
confidence intervals and regions for restricted ranges of the ROC curve.
The plotting methods therein use the base \proglang{R} plotting
functions to create nice displays of the curves along with shaded
confidence regions. The \pkg{plotROC} package uses the \pkg{ggplot2}
\citep{ggplot2} plotting package to create clear, informative ROC plots,
with interactive features for use on the web, and sensible defaults for
use in print.

@@

The panels of Figure \ref{figure1} illustrate the most common styles of
ROC curve plots, and the associated design elements. I favor the use of
gridlines and a diagonal reference line to facilitate accurate readings
off of the axes. Direct labels are preferred over legends because they
omit the additional cognitive step of matching line types or colors to
labels. The \pkg{plotROC} package additionally provides plotting of
cutoff values, which are displayed interactively with the web-based
output option, and direct labels for print use. Exact confidence regions
for points on the ROC curve are optionally calculated and displayed.
Additionally, the use of axis scales adjusted to be denser near the
margins 0 and 1 facilitates accurate reading of FPF and TPF values. In
medical applications, it is often necessary to have a very low FPF (less
than 10\%, for instance), therefore the smaller scales are useful for
accurately determining values near the margins. The next section details
the usage of the \pkg{plotROC} \proglang{R} package and these features.

@@

A \pkg{shiny} application \citep{shiny} was created in order to make the
features more accessible to non-\proglang{R} users. A limited subset of
the functions of \pkg{plotROC} can be performed on an example dataset or
on data that users upload to the website. Resulting plots can be saved
to the users' machine as a pdf or as a stand-alone html file. It can be
used in any modern web browser with no other dependencies at the website
here: http://sachsmc.shinyapps.io/plotROC.

@@

Users can install the latest version of \pkg{plotROC} from the
Comprehensive \proglang{R} Archive Network (CRAN). It can also be
downloaded or installed from https://github.com/sachsmc/plotROC, where
active development will take place. \pkg{plotROC} also requires at least
version 2.0.1 of \pkg{ggplot2} which is also available from CRAN.

\begin{Schunk}
\begin{Sinput}
R> install.packages(c("ggplot2", "plotROC"))
R> library(plotROC)
\end{Sinput}
\end{Schunk}

@@

As of version 2.0.1, the \pkg{ggplot2} package \citep{ggplot2} exports
the previously internal functions \code{Geom} and \code{Stat}. This
enables developers to create their own statistical tranformations
(stats) and geometric layers (geoms), while enjoying all of the other
features of \pkg{ggplot2}. I have implemented the empirical ROC curve
estimate and the calculation of exact confidence regions as statistical
transformations: \code{stat_roc} and \code{stat_rocci}, respectively. I
have also defined geometric layers for the ROC curve and confidence
regions for the ROC curve: \code{geom_roc} and \code{geom_rocci},
respectively. For further discussion and details of the grammar of
graphics as implemented in \pkg{ggplot2}, I refer readers to
\citet{wickham2010layered} and the \pkg{ggplot2} vignettes.

To use the ROC geometric layer, I use the \code{ggplot} function to
define the aesthetic mappings, and the \code{geom_roc} function to add
an ROC curve layer. The \code{geom_roc} function requires that the named
aesthetics \code{d} for disease status, and \code{m} for marker, be
present in the \code{aes} function call inside \code{ggplot}. By
default, the ROC geom and stat are linked, so that when \code{geom_roc}
is called, \code{stat_roc} does the computation, and when
\code{stat_roc} is called, \code{geom_roc} is used to plot the layer.
The disease status need not be coded as 0/1, but if it is not,
\code{stat_roc} assumes (with a warning) that the lowest value in sort
order signifies disease-free status.

@@

The same objects like \code{basicplot} with Roc and/or Rocci layers can
be treated like any other ggplot objects. They can be printed to display
the figure, and other layers can be added to the plot. I provide the
function \texttt{style\_roc()} which is a layer containing a theme,
modified gridlines, and axes. Adding the \texttt{style\_roc()} layer to
the ggplot object creates a plot with sensible defaults for use in
print. This function has options for the number and location of major
and minor breaks, addition of the diagonal guideline, axis labels, and
any theme object created for use with ggplot2 can be supplied.

@@

\textbackslash{}begin\{Schunk\} \textbackslash{}begin\{Sinput\}
R\textgreater{} library(survivalROC) R\textgreater{} survT \textless{}-
rexp(350, 1/5) R\textgreater{} cens \textless{}- rbinom(350, 1, .1)
R\textgreater{} M \textless{}- -8 * sqrt(survT) + rnorm(350, sd = survT)
R\textgreater{} sroc \textless{}- lapply(c(2, 5, 10), function(t)\{ +
stroc \textless{}- survivalROC(Stime = survT, status = cens, marker = M,
+ predict.time = t, method = ``NNE'', + span = .25 * 350\^{}(-.2)) +
data.frame(TPF = stroc{[}{[}``TP''{]}{]}, FPF = stroc{[}{[}``FP''{]}{]},
+ c = stroc{[}{[}``cut.values''{]}{]}, + time =
rep(stroc{[}{[}``predict.time''{]}{]}, +
length(stroc{[}{[}``FP''{]}{]}))) + \}) R\textgreater{} R\textgreater{}
sroclong \textless{}- do.call(rbind, sroc) R\textgreater{}
R\textgreater{} survplot \textless{}- ggplot(sroclong, aes(x = FPF, y =
TPF, label = c, color = time)) + + geom\_roc(labels = FALSE, stat =
``identity'') \textbackslash{}end\{Sinput\}
\textbackslash{}end\{Schunk\}

@@

\pkg{plotROC} makes interactive plots by first converting the
\code{ggplot} object into a scalable vector graphic (svg) object with
the \code{gridSVG::grid.export} function. This function maps each
element of the plot to a corresponding element of the svg markup
language. Interactivity is then added using \pkg{d3.js} and
\proglang{JavaScript} to manipulate those svg elements in response to
users' input. The main interactive feature is to display the cutoff
labels at the points on the ROC curve closest to the mouse cursor.

There are many ways to solve this with \pkg{d3.js}, but Voronoi polygons
are a convenient and efficient way to map the cursor location to
approximately the nearest point on the ROC curve. For the set of cutoff
points along the ROC curve, the \code{d3.geom.voronoi} function chain
computes a set of polygons overlaying the plotting region such that the
area of each polygon contains the region of the plot closest to it's
corresponding cutoff point. Hover events are bound to the polygons so
that when the mouse cursor moves around the plotting region, the closest
point on the ROC curve is made visible. Similarly, click events are
bound to the polygons so that the appropriate confidence region is made
visible upon clicking. The svg code and all necessary
\proglang{JavaScript} code is returned in the character string provided
by \code{export_interactive_roc}.

This approach is similar to what is done in the \pkg{gridSVG}
\code{grid.animate} function, which uses the svg \code{<animate />}
tags. However, \pkg{d3.js} provides a much richer set of features. There
are several other \proglang{R} packages that aim to create interactive
figures. The authors of \pkg{animint} \citep{animint} created an
extensive \proglang{JavaScript} library that creates plots in a similar
way as \pkg{ggplot2}. A set of interactive features can be added to
plots using \pkg{d3.js}. \pkg{ggvis} \citep{ggvis}, \pkg{rCharts}
\citep{rcharts}, and the more recently released \pkg{htmlwidgets}
\citep{htmlwidgets} all leverage existing charting libraries written in
\proglang{JavaScript}. \pkg{qtlcharts} \citep{qtlcharts} uses a set of
custom \proglang{JavaScript} and \pkg{d3.js} functions to visualize data
from genetic experiments. Their general approach is to manipulate the
data and record plotting options in \proglang{R}, and then pass those
objects to the charting libraries or functions that handle the rendering
and interactivity. \pkg{plotROC} lets \proglang{R} do the rendering,
allowing the figures to be consistent across print and web-based media,
and retaining the distinctive \proglang{R} style. This also allows users
to manipulate the figures directly in \proglang{R} to suit their needs,
using tools that are more accessible and familiar to most \proglang{R}
users. Then, the \proglang{JavaScript} adds a layer of interactivity to
the rendered figures.

@@

\begin{Schunk}
\begin{Sinput}
R> sessionInfo()
\end{Sinput}
\begin{Soutput}
R version 3.2.4 (2016-03-10)
Platform: x86_64-apple-darwin13.4.0 (64-bit)
Running under: OS X 10.11.4 (El Capitan)

@@

other attached packages:
[1] survivalROC_1.0.3 plotROC_2.0.1     ggplot2_2.1.0     xtable_1.8-2     
[5] stringr_1.0.0     knitr_1.13

loaded via a namespace (and not attached):
 [1] Rcpp_0.12.5       digest_0.6.9      grid_3.2.4       
 [4] plyr_1.8.3        gtable_0.2.0      formatR_1.4      
 [7] magrittr_1.5      evaluate_0.9      scales_0.4.0     
[10] highr_0.6         stringi_1.0-1     tikzDevice_0.10-1
[13] labeling_0.3      tools_3.2.4       munsell_0.4.3    
[16] colorspace_1.2-6  filehash_2.3     
\end{Soutput}
\end{Schunk}
